Fast, Scalable Phrase-Based SMT Decoding

### 2016-03-03 acl.2016/acl2016.tex
acl paper
Couple typos

% Author information can be set in various styles:
% For several authors from the same institution:
% \author{Author 1 \and ... \and Author n \\
%         Address line \\ ... \\ Address line}
% if the names do not fit well on one line use
%         Author 1 \\ {\bf Author 2} \\ ... \\ {\bf Author n} \\
% For authors from different institutions:
% \author{Author 1 \\ Address line \\  ... \\ Address line
%         \And  ... \And
%         Author n \\ Address line \\ ... \\ Address line}
% To start a seperate ``row'' of authors use \AND, as in
% \author{Author 1 \\ Address line \\  ... \\ Address line
%         \AND
%         Author 2 \\ Address line \\ ... \\ Address line \And
%         Author 3 \\ Address line \\ ... \\ Address line}
% If the title and author information does not fit in the area allocated,
% place \setlength\titlebox{<new height>} right after
% at the top, where <new height> can be something larger than 2.25in
\author{Hieu Hoang\\
	    Moses Machine Translation CIC\\
	    {\tt hieu@moses-mt.org}
	  \And
	Nicolay Bogoychev\\
  	University of Edinburgh\\
  	10 Crichton Street\\
  	Edinburgh, Scotland, EH10 9AB\\
  {\tt s1031254@sms.ed.ac.uk}
	  \And
	Lane Schwartz\\
  	University of Illinois\\
  {\tt lanes@illinois.edu}
	  \AND
	Kenneth Heafield\\
  	University of Edinburgh\\
  {\tt kheafiel@inf.ed.ac.uk}
	  \And
	Marcin Junczys-Dowmunt\\
	Faculty of Mathematics and Computer Science \\
	Adam Mickiewicz University\\
  {\tt junczys@amu.edu.pl}
	}

@@

~\newcite{Heafield-mtplz} is perhaps closest in intent to this work. This takes a holistic approach to decoding, describing a novel decoding algorithm which is fis focused on better decoding speed. It also describes a number of implementation details for faster decoding. However, the decoding algorithm is only able to incorporate one stateful feature function which precludes some of the useful decoding configurations which contains multiple stateful feature functions. It does not include a load-on-demand phrase table, therefore, cannot be used in a commercial environment where phrase-table has not be filtered with a know test set for any realistic size phrase-table. Neither did this paper analyze the scalability of their work to multicore servers.

@@

We trained a phrase-based system using the Moses toolkit with standard settings. The training data consisted of most of the publicly available Arabic-English data from Opus~\cite{tiedemann2012parallel} containing over 69 million parallel sentences, and tuned on a held out set. The phrase-table was then pruned, keeping only the top 100 entries per source phrase, according to $p(t|s)$. All models files were then binarized; the language models were binaized using KenLM~\cite{Heafield-kenlm}, the phrase table using the Probing phrase-table, lexicalized reordering model using the compact datastructure. These binary formats were choosen for their best-in-class multithreaded performance. Table~\ref{tab:model-files} gives details of the resultant sizes of the model files. For verification with a different dataset, we also occasionally used a second system trained on the French-English Europarl corpus (2m parallel sentences). 
\begin{table}[h]
\begin{center}
\begin{tabular}{|l|c|c|} \hline
		& ar-en	& fr-en \\ \hline
Phrase table  	& 17 	& 5.8 \\
Language model 	& 3.1  	& 1.8 \\ 
Lex re. model	& 2.3	& 637MB \\ \hline
\end{tabular}
\end{center}
\caption{Model sizes in GB}
\label{tab:model-files}
\end{table}
For testing decoding speed, we used a subset of the training data, Table~\ref{tab:test-sets}. The two test scenarios have differing characterics that we are interested in analyzing, ar-en have short sentences with large models while fr-en have overly long sentences with smaller models. Where we need to compare model scores, we used held out test sets.

>>>>

\author{Hieu Hoang\\
	    Moses Machine Translation CIC\\
	    {\tt hieu@moses-mt.org}
	  \And
	Nicolay Bogoychev\\
  	University of Edinburgh\\
  	10 Crichton Street\\
  	Edinburgh, Scotland, EH10 9AB\\
  {\tt s1031254@sms.ed.ac.uk}
	  \And
	Lane Schwartz\\
  	University of Illinois\\
  {\tt lanes@illinois.edu}
	  \AND
	Kenneth Heafield\\
  	University of Edinburgh\\
  {\tt kheafiel@inf.ed.ac.uk}
	  \And
	Marcin Junczys-Dowmunt\\
	Faculty of Mathematics and Computer Science \\
	Adam Mickiewicz University\\
  {\tt junczys@amu.edu.pl}
	}

@@

~\newcite{Heafield-mtplz} is perhaps closest in intent to this work. This takes a holistic approach to decoding, describing a novel decoding algorithm which is focused on better decoding speed. It also describes a number of implementation details for faster decoding. However, the decoding algorithm is only able to incorporate one stateful feature function which precludes some of the useful decoding configurations which contains multiple stateful feature functions. It does not include a load-on-demand phrase table, therefore, cannot be used in a commercial environment where phrase-table has not be filtered with a know test set for any realistic size phrase-table. Neither did this paper analyze the scalability of their work to multicore servers.

@@

We trained a phrase-based system using the Moses toolkit with standard settings. The training data consisted of most of the publicly available Arabic-English data from Opus~\cite{tiedemann2012parallel} containing over 69 million parallel sentences, and tuned on a held out set. The phrase-table was then pruned, keeping only the top 100 entries per source phrase, according to $p(t|s)$. All models files were then binarized; the language models were binarized using KenLM~\cite{Heafield-kenlm}, the phrase table using the Probing phrase-table, lexicalized reordering model using the compact datastructure. These binary formats were choosen for their best-in-class multithreaded performance. Table~\ref{tab:model-files} gives details of the resultant sizes of the model files. For verification with a different dataset, we also occasionally used a second system trained on the French-English Europarl corpus (2m parallel sentences). 
\begin{table}[h]
\begin{center}
\begin{tabular}{|l|c|c|} \hline
		& ar-en	& fr-en \\ \hline
Phrase table  	& 17 	& 5.8 \\
Language model 	& 3.1  	& 1.8 \\ 
Lex re. model	& 2.3	& 637MB \\ \hline
\end{tabular}
\end{center}
\caption{Model sizes in GB}
\label{tab:model-files}
\end{table}
For testing decoding speed, we used a subset of the training data, Table~\ref{tab:test-sets}. The two test scenarios have differing characterics that we are interested in analyzing, ar-en have short sentences with large models while fr-en have overly long sentences with smaller models. Where we need to compare model scores, we used held out test sets.
